Regular singular Volterra equations on complex domains

### 2023-08-08 reg-sing-volterra.tex
Mark completed tasks on to-do list

\item \textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.
\item \textit{(Aaron)} Finish introduction

@@

@@

        \item \textit{(Aaron)} Add proofs of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra} to Section~\ref{sec:existence and uniqueness}

>>>>

\item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
    \item Proofread and drop old version.
\item \textcolor{gray}{\textit{(Aaron)} Finish introduction}

@@

\item \textit{(Veronica)} Revise introduction, if desired.

@@

        \item \textcolor{gray}{\textit{(Aaron)} Add proof of Lemma~\ref{lem:perturbed_volterra} to Section~\ref{sec:existence and uniqueness}}
        \item \textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}
